---
title: "5 Most Common Turtle Species Globally & the Counties They Are Most Prevalent In"
output: github_document
---


## Abstract

     Turtles are among one of the oldest groups of reptiles that date back millions of years. There are over 300 species of turtles that reside in varying climates and environments all around the world. I will investigate which five turtle species are most commonly found globally and in which countries they are most prevalent. In an effort to find an answer to my question, I will be utilizing the data found in GBIF [Global Biodiversity Information Facility] for turtle occurrences filtered by machine and human observations. I plan to perform an exploratory data analysis of turtle occurrences in order to compare the variables in the data set. With my anticipated results, researchers and other turtle scientists may be able to also utilize this information to help compare to future observations of turtle occurrences and determine if they have increased or decreased in numbers in specific countries globally.

```{r,message=FALSE,warning=FALSE}
 
```


## Introduction

Sentence Here.


## Methods

Sentence Here.

```{r cars}
summary(cars)
```


## References

Cite 3 sources here.

```{r pressure, echo=FALSE}
plot(pressure)
```


