---
title: "5 Most Common Turtle Species Globally & the Counties They Are Most Prevalent In"
output: github_document
---


## Abstract

Turtles are among one of the oldest 
groups of reptiles that date back millions 
of years. There are over 300 species of 
turtles that reside in varying climates 
and environments all around the world. 
I will investigate which five turtle 
species are most commonly found globally 
and in which countries they are most 
prevalent. In an effort to find an answer 
to my question, I will be utilizing the 
data found in GBIF [Global Biodiversity 
Information Facility] for turtle 
occurrences filtered by machine and 
human observations. I plan to perform an 
exploratory data analysis of turtle 
occurrences in order to compare the 
variables in the data set. With my 
anticipated results, researchers and 
other turtle scientists may be able to 
also utilize this information to help 
compare to future observations of turtle 
occurrences and determine if they have 
increased or decreased in numbers in 
specific countries globally.

```{r,message=FALSE,warning=FALSE}
 
```


## Introduction

background (context), your question, and a sentence saying how you plan to answer your question. You should cite at least three (3) articles in peer-reviewed journals. Use the format (Merkord 2019) when citing.


## Methods

two paragraphs. In the first, explain where the dataset comes from, including the necessary citation(s). Briefly describe how the data was collected. After citing the data source, explain what the data consists of (list the variables, and describe what observations (rows) represent. 

The second paragraph in your methods should give a brief overview of how you analyzed the data. 

```{r}
ggplot(data = Cheloniidae) + geom_bar(mapping = aes(x = species)) + coord_flip()
```



## References

GBIF Database - 2 sets

[GBIF.org (01 April 2019) Cheloniidae - occurrences Download](https://doi.org/10.15468/dl.ilhrhu) 
(Involved datasets 271)
[Cheloniidae - occurrences 108,250](https://www.gbif.org/occurrence/search?taxon_key=9413)

[GBIF.org (01 April 2019) Dermochelyidae - occurrences Download](https://doi.org/10.15468/dl.hi499f) 
(Involved datasets 178)
[Dermochelyidae - occurrences 7,195](https://www.gbif.org/occurrence/search?taxon_key=5464)


+3 more citations

```{r pressure, echo=FALSE}
plot(pressure)
```


